\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,top=0.6in,bottom=0.55in,left=0.65in,right=0.65in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{xcolor}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=1.2em,itemsep=2pt,topsep=2pt}

\definecolor{rulegray}{gray}{0.82}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\color{rulegray}\titlerule]
\titlespacing*{\section}{0pt}{22pt}{4pt}

\begin{document}

\begin{center}
{\LARGE\bfseries SAUD KHAN ABBAS}\\[3pt]
{\large SOFTWARE ENGINEERING STUDENT}\\[7pt]

Bangalore, India \;|\;
8951845145 \;|\;
\href{mailto:saudkhanabbas@gmail.com}{saudkhanabbas@gmail.com}
\;|\;
\href{https://github.com/SaudKhanAbbas}{github.com/SaudKhanAbbas}
\;|\;
\href{https://linkedin.com/in/saud-khan-abbas}{linkedin.com/in/saud-khan-abbas}
\end{center}

\section*{PROFILE}
Engineering student interested in AI engineering, intelligent systems, finance, and entrepreneurship. Building strong foundations in Python, Java, data structures \& algorithms, and software engineering through hands-on projects. At Kalvium, I work on industry-driven coursework focused on full-stack development, backend systems, AI/ML fundamentals, and scalable software engineering.

\section*{SKILLS}
\textbf{Programming Languages:} Python, Java, JavaScript\\
\textbf{Frontend:} React.js, HTML5, CSS3, Tailwind CSS\\
\textbf{Backend:} Node.js, Express.js, REST APIs\\
\textbf{Database:} MongoDB\\
\textbf{Developer Tools:} Git, GitHub, Docker, Postman, VS Code\\
\textbf{Core Concepts:} Data Structures \& Algorithms, OOP, Authentication \& Authorization, Problem Solving

\section*{PROJECTS}

\textbf{Revion — Motorcycle Management Platform} \hfill \textit{React.js | Node.js | Express | MongoDB}

\href{https://github.com/SaudKhanAbbas/revion}{github.com/SaudKhanAbbas/revion}

\begin{itemize}
\item Designed and developed a MERN-based motorcycle management platform for tracking maintenance, expenses and service history.
\item Built JWT authentication, protected REST APIs and MongoDB-backed data models.
\item Developed responsive React interfaces with reusable components and clean UI architecture.
\end{itemize}

\textbf{Mini BitTorrent Client} \hfill \textit{Python | Sockets | SHA-1}

\href{https://github.com/SaudKhanAbbas/bittorrent-protocol-explorer}{github.com/SaudKhanAbbas/bittorrent-protocol-explorer}

\begin{itemize}
\item Implemented core BitTorrent protocol functionality from scratch in Python.
\item Parsed torrent metadata, communicated with trackers and established peer handshakes.
\item Verified downloaded pieces using SHA-1 integrity checks before assembling files.
\end{itemize}

\section*{EDUCATION}

\begin{tabularx}{\textwidth}{Xr}
\textbf{Alliance University × Kalvium} & \textbf{2025--2029}\\
Bachelor of Technology in Computer Science Engineering & \\
Semester 1 SGPA: \textbf{9.2 / 10} &
\end{tabularx}

\section*{COURSEWORK}
\begin{tabularx}{\textwidth}{X X}
$\bullet$ Data Structures \& Algorithms & $\bullet$ Backend Development\\
$\bullet$ Full Stack Web Development & $\bullet$ REST API Development\\
$\bullet$ Database Systems & $\bullet$ Git \& GitHub\\
$\bullet$ Object-Oriented Programming & $\bullet$ Software Engineering Fundamentals
\end{tabularx}

\section*{LANGUAGES}
English --- Fluent \hfill Hindi --- Fluent \hfill Kannada --- Native

\end{document}
